---
title: "GML_Main"
author: "Devin Frost"
date: "2024-03-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(data.table)
```

# Getting the data

I recommend not running this next chuck, as it takes a lot of RAM and CPU
```{r include=FALSE}
Raw_LCI_Data <- read_csv("game_data_public.LCI.PremierDraft.csv")
DowntoDecks <- Raw_LCI_Data |> select(won, matches("deck_"))
fwrite(DowntoDecks, file = "DowntoDecks", col.names = T, showProgress = T)

```


# Data Exploration


```{r}
DowntoDecks <- read_csv("DowntoDecks.csv")
#DowntoDecks |> count(won)

```

#Simplified card comparision
  
This defines a function that compares two given cards and spits out their winrate. Returns 0 if they are never played with each other. The length thing is a bit hacky tbh, but it works.
```{r}
winrate <- function (c1,c2){
  temp <- DowntoDecks %>% filter(.[[c1]] > 0 & .[[c2]] > 0) %>% count(won)
  if(length(as.matrix(temp)) != 4) {
    return(0)
  }
  return(temp[[2,2]]/(temp[[2,2]] + temp[[1,2]]))
}

#winrate function, card 1, card 2
#only comparing the first card, Abrade to all OTHER cards 
#simplified for my poor laptop
AbradeX <- mapply(winrate, 3, 2:ncol(DowntoDecks), SIMPLIFY = T)
```

DONT RUN THIS. Builds the adjancency matrix for the down to decks data, then writes it to a csv so we don't need to do it again. took at least more than 30 minutes. 
```{r}
RESULT <- data.frame()

for (i in 2:ncol(DowntoDecks)) {
  RESULT <- rbind(RESULT,
                  mapply(winrate, i, 2:ncol(DowntoDecks), SIMPLIFY = T))
}

fwrite(RESULT, file = "DecksGraph.stl", col.names = F, showProgress = T)

```

Making gods most basic adjacency matrix
```{r}
BasicAdjMatrix <- matrix(nrow = 291, ncol = 291)

for (i in 1:nrow(RESULT)) {
  for (j in 1:ncol(RESULT)) {
    if(RESULT[[i,j]] > 0) {
      BasicAdjMatrix[i,j] <- 1
    } else {
      BasicAdjMatrix[i,j] <- 0
    }
  }
}

```



```{r}
library(igraph)

graphgraph <- graph_from_adjacency_matrix(as.matrix(BasicAdjMatrix,"adjacency"))
plot.igraph(graphgraph,layout = layout_with_lgl(graphgraph), 
            edge.arrow.size=0.5, vertex.size = 10, vertex.label.cex = 0.1)

```







## looking at the
```{r}
deck_mat <- DowntoDecks[,-1] |> as.matrix() |> as.vector()
zeros <- deck_mat == 0 
deck_mat[zeros] <- NA

deck_mat |> hist()

```



```{python}
for i in range(100):
  print(i)
```

